---
title: "appender"
author: "Othon Hamill"
date: "12/7/2018"
output: word_document
---

The purpose of this file is to add new match data onto the profiles of each player

###########Functions unique to this file#####################

```{r}
#Date should be in a ddmmmyyy i.e. 4jan2018 or 24feb2017
Appender<-function(PlayerID, Old, New, Date, FinalResult, BYUHand, OppHand){

  N<-dim(New)[1]
  Date<-as.Date(Date,"%d%b%Y")
  ToInput <- data.frame(PlayerID=rep(PlayerID,times=N),
                     SeasonID=rep("-",times=N),
                     MatchID=rep("-",times=N),
                     Date=rep(Date,times=N),
                     HomeAway=rep("Home",times=N),
                     WinLoss=rep(FinalResult,times=N),
                     PlayerStyle=rep("-",times=N),
                     PlayerLR=rep(BYUHand,times=N),
                     OppStyle=rep("-",times=N),
                     OppLR=rep(OppHand,times=N),
                     PlayerSets=New$PlayerSets,
                     OppSets=New$OpponentSets,
                     GameID=rep("-",times=N),
                     PlayerGames=New$PlayerGames,
                     OppGames=New$OpponentGames,
                     Server=New$Server,
                     PointID=rep("-",times=N),
                     PlayerPoints=New$PlayerPoints,
                     OppPoints=New$OpponentPoints,
                     ServeResult=New$ServeResult,
                     ServeLocation=New$ServeLocation,
                     ReturnLocation=New$Returns,
                     Result=New$PointResult,
                     PointWinner=New$PointWinner,
                     FinalShotType=New$ShotType,
                     FinalForeBack=New$ForeBack,
                     FinalCrossLine=New$CrossLine,
                     PenumltimateShotType=rep("-",times=N),
                     PenumltimateForeBack=rep("-",times=N),
                     PenumltimateCrossLine=rep("-",times=N),
                     NetPlay=rep("-",times=N),
                     PointLength=New$PointLength,
                     ErrorPosition=New$ErrorPosition,
                     Comments=New$Comment,
                 stringsAsFactors=FALSE)
  Appended<-rbind(Old,ToInput)
  return(Appended)
}
```

Now we build an empty set to begin the appending process
```{r}
EmptySet <- data.frame(PlayerID=character(),
                     SeasonID=character(),
                     MatchID=character(),
                     Date=as.Date(character()),
                     HomeAway=character(),
                     WinLoss=character(),
                     PlayerStyle=character(),
                     PlayerLR=character(),
                     OppStyle=character(),
                     OppLR=character(),
                     PlayerSets=numeric(),
                     OppSets=numeric(),
                     GameID=character(),
                     PlayerGames=numeric(),
                     OppGames=numeric(),
                     Server=character(),
                     PointID=character(),
                     PlayerPoints=numeric(),
                     OppPoints=numeric(),
                     ServeResult=character(),
                     ServeLocation=character(),
                     ReturnLocation=character(),
                     Result=character(),
                     PointWinner=character(),
                     FinalShotType=character(),
                     FinalForeBack=character(),
                     FinalCrossLine=character(),
                     PenumltimateShotType=character(),
                     PenumltimateForeBack=character(),
                     PenumltimateCrossLine=character(),
                     NetPlay=character(),
                     PointLength=character(),
                     ErrorPosition=character(),
                     Comments=character(),
                 stringsAsFactors=FALSE)
```

#########        Here's the actual workspace       ##############
Here we'll create the datasets we'll be using and constantly updating.

Here we'll add in and separate the 2018 Women's Data Parker has sent in from last year. Turns out it completely overlaps with the WTennisData dataset. that worked out to be all of the january 26th matches as contained in Parker's dataset. 
```{r}
WComb2018o<-read.csv("wcomb.csv")
WComb2018<-WComb2018o[,c(17,3,1,11,12,14:16, 18:30)]
colnames(WComb2018)<-colnames(WTennisStats)

HKaur1<-WComb2018[1:71,]
HKaur<-Appender("Hermehr Kaur", Old=EmptySet, New=HKaur1, "26jan2018", "Win", "R", "R")
HKaur2<-WComb2018[1517:1563,]
HKaur<-Appender("Hermehr Kaur", Old=HKaur, New=HKaur2, "2mar2018", "-", "R", "R")
write.csv(HKaur,'HKaur.csv')

KCusick1<-WComb2018[72:160,]
KCusick<-Appender("Kate Cusick", Old=EmptySet, New=KCusick1, "26jan2018", "Win", "R", "R")
KCusick2<-WComb2018[1564:1726,]
KCusick<-Appender("Kate Cusick", Old=KCusick, New=KCusick2, "16feb2018", "Loss", "R", "R")
write.csv(KCusick,'KCusick.csv')

SSmith1<-WComb2018[161:262,]
SSmith<-Appender("Samantha Smith", Old=EmptySet, New=SSmith1, "26jan2018", "Win", "R", "R")
write.csv(SSmith,'SSmith.csv')

AAbramyan1<-WComb2018[263:384,]
AAbramyan<-Appender("Anastasia Abramyan", Old=EmptySet, New=AAbramyan1, "26jan2018", "Win", "R", "R")
AAbramyan2<-WComb2018[477:625,]
AAbramyan<-Appender("Anastasia Abramyan", Old=AAbramyan, New=AAbramyan2, "16feb2018", "Loss", "R", "R")
AAbramyan3<-WComb2018[1898:2083,]
AAbramyan<-Appender("Anastasia Abramyan", Old=AAbramyan, New=AAbramyan3, "24mar2018", "Win", "R", "R")
write.csv(AAbramyan,'AAbramyan.csv')

MJones1<-WComb2018[385:476,]
MJones<-Appender("Mayci Jones", Old=EmptySet, New=MJones1, "26jan2018", "Win", "R", "R")
MJones2<-WComb2018[954:1062,]
MJones<-Appender("Mayci Jones", Old=MJones, New=MJones2, "16feb2018", "Loss", "R", "R")
MJones3<-WComb2018[1174:1290,]
MJones<-Appender("Mayci Jones", Old=MJones, New=MJones3, "3mar2018", "Loss", "R", "R")
MJones4<-WComb2018[1291:1433,]
MJones<-Appender("Mayci Jones", Old=MJones, New=MJones4, "2mar2018", "-", "R", "R")
MJones5<-WComb2018[1727:1897,]
MJones<-Appender("Mayci Jones", Old=MJones, New=MJones5, "24mar2018", "Loss", "R", "R")
write.csv(MJones,'MJones.csv')

PMalykh1<-WComb2018[626:715,]
PMalykh<-Appender("Polina Malykh", Old=EmptySet, New=PMalykh1, "26jan2018", "Win", "R", "R")
PMalykh2<-WComb2018[716:850,]
PMalykh<-Appender("Polina Malykh", Old=PMalykh, New=PMalykh2, "16feb2018", "Win", "R", "R")
write.csv(PMalykh,'PMalykh.csv')

TBeckman1<-WComb2018[851:953,]
TBeckman<-Appender("TBeckman", Old=EmptySet, New=TBeckman1, "16feb2018", "-", "R", "R")

MAlmeida1<-WComb2018[1063:1173,]
MAlmdeida<-Appender("Madeline Almeida", Old=EmptySet, New=MAlmeida1, "3mar2018", "-", "R", "R")
MAlmeida2<-WComb2018[1434:1516,]
MAlmdeida<-Appender("Madeline Almeida", Old=MAlmdeida, New=MAlmeida2, "18mar2018", "Win", "R", "R")
```

