---
title: "Clutch Work"
author: "Othon Hamill"
date: "October 24, 2018"
output: word_document
---

```{r}
#########################TO DO LIST############################
#How are we going to deal with returns hit into the net? 

#We need to take out possible tieBreaks since they mess with Data

#We have the Data properly corrected for the set set/game Score corrections, but not for any possible match/set Score issues 
```

```{r}
#call our necessary libraries
library(alr3)
library(MASS)
library(dplyr)
library(future.apply)
library(furrr)
library(sass)
library(gt)
library(tictoc)
library(openxlsx)
```

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Functions~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

Set Score Corrector, for those situations where the set Score doesn't get set back to 0-0 after a set is won
```{r}
SetScoreCorrector<-function(Data){
  N<-dim(Data)[1]
  Errors<-rep(0,times=N)
  
  #Here's our work for a win on the players side not being counted correctly
    for (i in 1:N){
        Errors[i]<- (Data$PlayerGames[i] >= 6 & Data$OppGames[i] < 5)
    }
  
    #here we correct the game/set Scores. We make the assumption our Data has the sets correct
    Data$PlayerGames<-Data$PlayerGames-Errors*(6)
  
  #here's our work for when  
    
    return(Data)
}
```



Situational Weights adds an additional column which gives a weight Score for each point
40-00 gets a .3 multiplier, 40-15 a .7, 40-30 a 1.0, Deuce a 2x
4-4 and 5-5 get a x1.5 multiplier
Set Points get x2
Second Set Match Points get a x3 Multiplier
Third Set Match Points get a x3 Multiplier

5-4, 4-5, 6-5 and 5-6 gets a +1


```{r}
SituationalWeights<-function(Data){
  N<-dim(Data)[1]
  Multiplier<-rep(0,times=N)
  
  #Game Points by Score weight
  for (i in 1:N){
    if(Data$PlayerPoints[i] == 0 & Data$OppPoints[i] == 3){Multiplier[i]<-.3}
    if(Data$OppPoints[i] == 0 & Data$PlayerPoints[i] == 3){Multiplier[i]<-.3}
    if(Data$PlayerPoints[i] == 1 & Data$OppPoints[i] == 3){Multiplier[i]<-.7}
    if(Data$OppPoints[i] == 1 & Data$PlayerPoints[i] == 3){Multiplier[i]<-.7}
    if(Data$PlayerPoints[i] == 2 & Data$OppPoints[i] == 3){Multiplier[i]<-1}
    if(Data$OppPoints[i] == 2 & Data$PlayerPoints[i] == 3){Multiplier[i]<-1}
    if(Data$PlayerPoints[i] == 3 & Data$OppPoints[i] == 3){Multiplier[i]<-2}
  }
  
  #Game points under duress at 4-4 or 5-5 set Score. High Pressure already keeps only game points
  for (i in 1:N){
    if(Data$PlayerGames[i] == 4 & Data$OppGames[i] == 4){Multiplier[i]<-Multiplier[i]*1.5}
    if(Data$OppGames[i] == 5 & Data$PlayerGames[i] == 5){Multiplier[i]<-Multiplier[i]*1.5}
  }

  #Set Points, 1st set about to be won by either or second about to be won by the loser of the first set
  for (i in 1:N){
    #Opp about to win the set
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    #player about to win the set
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*2}
  }
  
  #Match Points in the second set
  for(i in 1:N){
    #player about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*3}
    #Opponent about to win
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
  }
  
  #Match Points in the Third set
  for(i in 1:N){
    #player about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*5}
    #Opponent about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
  }
  
  return(Multiplier)
}

```



PServingOnly function filters out Opponents, leaving just BYU serving
```{r}
PServingOnly<-function(RawData){
  Joint<-filter(RawData,RawData$Server=="P")
}
```

HighPressure function keeps only possible Clutch points (a Break or Hold point)
```{r}
HighPressure<-function(RawData){
  #just Clutch points, no sorting for Server
HP<-rbind(
    RawData[(RawData$PlayerPoints == 0 & RawData$OppPoints == 3),],
    RawData[(RawData$PlayerPoints == 1 & RawData$OppPoints == 3),],
    RawData[(RawData$PlayerPoints == 2 & RawData$OppPoints == 3),],
    RawData[(RawData$PlayerPoints == 3 & RawData$OppPoints == 3),],
    RawData[(RawData$PlayerPoints == 3 & RawData$OppPoints == 2),],
    RawData[(RawData$PlayerPoints == 3 & RawData$OppPoints == 1),],
    RawData[(RawData$PlayerPoints == 3 & RawData$OppPoints == 0),])
  return(HP)
}
```

LowPressure function keeps everything but Clutch points
```{r}
LowPressure<-function(RawData){
  #just Clutch points, no sorting for Server
LP<-RawData[(RawData$PlayerPoints != 3 & RawData$OppPoints != 3),]
  return(LP)
}
```

Serving Scoring function
```{r}
ServingScore<-function(Dataset, W=c(1,-1,0)){
  Clutch<-rbind(filter(Dataset,Dataset$PointWinner=="P" & Dataset$PointLength=="S" & Dataset$Result %in% c("W","F") & Dataset$Server=="P"), filter(Dataset, Dataset$Result=="A" & Dataset$Server=="P"))
  Choke<-rbind(filter(Dataset,Dataset$PointWinner=="O" & Dataset$PointLength=="S" & Dataset$Result %in% c("W","F") & Dataset$Server=="P"), filter(Dataset, Dataset$Result=="D" & Dataset$Server=="P"))
  Null<-rbind(filter(Dataset, Dataset$ServeResult %in% c("F","S") & Dataset$PointLength %in% c("M","L") & Dataset$Server=="P"))

    Score<-c(sum(Clutch$SituationalWeight)*W[1]+sum(Choke$SituationalWeight)*W[2]+sum(Null$SituationalWeight)*W[3])
  
  N<-dim(rbind(Clutch,Choke,Null))[1]
  
  Ans<-list(Score,N)
  
  return(Ans)
}
```

Play Scoring function
```{r}
PlayScore<-function(Dataset, W=c(1,-1,0)){
  Clutch<-filter(Dataset,Dataset$PointWinner=="P" & Dataset$Result %in% c("W","F"))
  Choke<-filter(Dataset,Dataset$PointWinner=="O" & Dataset$Result == "U")
  Null<-rbind(filter(Dataset,Dataset$PointWinner=="P" & Dataset$Result == "U"), filter(Dataset,Dataset$PointWinner=="O" & Dataset$Result %in% c("W","F")))
  #we can add in modifiers if we so desire here
  Score<-c(sum(Clutch$SituationalWeight)*W[1]+sum(Choke$SituationalWeight)*W[2]+sum(Null$SituationalWeight)*W[3])
  
  N<-dim(rbind(Clutch,Choke,Null))[1]
  
  Ans<-list(Score,N)
  
  return(Ans)
}
```

Serving + Play Clutch Score
```{r}
ClutchScore<-function(Dataset){
  Score<-PlayScore(Dataset)[[1]]+ServingScore(Dataset)[[1]]
  N<-PlayScore(Dataset)[[2]]+ServingScore(Dataset)[[2]]
  Ans<-list(Score,N)
  return(Ans)
}
```


Low Pressure Column (No game points of any kind)
```{r}
LPcolumn<-function(Dataset){
  LPData<-LowPressure(Dataset)
  
  LPServingScore<-ServingScore(LPData)[[1]]
  LPPlayScore<-PlayScore(LPData)[[1]]
  LPClutchScore<-ClutchScore(LPData)[[1]]
  LPColumn<-c(LPServingScore,LPPlayScore,LPClutchScore)
  
  LPServingN<-ServingScore(LPData)[[2]]
  LPPlayN<-PlayScore(LPData)[[2]]
  LPClutchN<-ClutchScore(LPData)[[2]]
  LPN<-c(LPServingN,LPPlayN,LPClutchN)
  
  Ans<-list(LPColumn,LPN)
  
  return(Ans)
}
```


BYU Hold Point Calculating function
```{r}
BYUHoldColumn<-function(Dataset){
  #build the BYU Holding Data frame including the deuce points
  BYUHolddf<-rbind(
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 3) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 2) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 1) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 0) & Dataset$Server== "P",])
  BYUHoldServingScore<-ServingScore(BYUHolddf)
  BYUHoldPlayScore<-PlayScore(BYUHolddf)
  BYUHoldClutchScore<-ClutchScore(BYUHolddf)
  BYUHoldScores<-c(BYUHoldServingScore[[1]],BYUHoldPlayScore[[1]],BYUHoldClutchScore[[1]])
  N<-c(BYUHoldServingScore[[2]],BYUHoldPlayScore[[2]],BYUHoldClutchScore[[2]])
  Ans<-list(BYUHoldScores,N)
  return(Ans)
}
```

BYU being broken Point Calculating function
```{r}
BYUBreakColumn<-function(Dataset){
  #build the BYU to be broken Data frame including the deuce points
  BYUBreakdf<-rbind(
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 3) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 2 & Dataset$OppPoints == 3) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 1 & Dataset$OppPoints == 3) & Dataset$Server== "P",],
    Dataset[(Dataset$PlayerPoints == 0 & Dataset$OppPoints == 3) & Dataset$Server== "P",])
  BYUBreakServingScore<-ServingScore(BYUBreakdf)
  BYUBreakPlayScore<-PlayScore(BYUBreakdf)
  BYUBreakClutchScore<-ClutchScore(BYUBreakdf)
  BYUBreakScores<-c(BYUBreakServingScore[[1]],BYUBreakPlayScore[[1]],BYUBreakClutchScore[[1]])
  N<-c(BYUBreakServingScore[[2]],BYUBreakPlayScore[[2]],BYUBreakClutchScore[[2]])
  Ans<-list(BYUBreakScores,N)
  return(Ans)
}
```

Opp Hold Point Calculating function
```{r}
OppHoldColumn<-function(Dataset){
  #build the Opp Holding Data frame including the deuce points
  OppHolddf<-rbind(
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 3) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 2 & Dataset$OppPoints == 3) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 1 & Dataset$OppPoints == 3) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 0 & Dataset$OppPoints == 3) & Dataset$Server== "O",])
  OppHoldPlayScore<-PlayScore(OppHolddf)
  OppHoldClutchScore<-ClutchScore(OppHolddf)
  OppHoldScores<-c(OppHoldPlayScore[[1]],OppHoldClutchScore[[1]])
  N<-c(OppHoldPlayScore[[2]],OppHoldClutchScore[[2]])
  Ans<-list(OppHoldScores,N)
  return(Ans)
}
```

Opp being broken Point Calculating function
```{r}
OppBreakColumn<-function(Dataset){
  #build the Opp Breaking Data frame including the deuce points
  OppBreakdf<-rbind(
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 3) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 2) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 1) & Dataset$Server== "O",],
    Dataset[(Dataset$PlayerPoints == 3 & Dataset$OppPoints == 0) & Dataset$Server== "O",])
  OppBreakPlayScore<-PlayScore(OppBreakdf)
  OppBreakClutchScore<-ClutchScore(OppBreakdf)
  OppBreakScores<-c(OppBreakPlayScore[[1]],OppBreakClutchScore[[1]])
  N<-c(OppBreakPlayScore[[2]],OppBreakClutchScore[[2]])
  Ans<-list(OppBreakScores,N)
  return(Ans)
}
```

Raw Combo makes the Raw combo column in the Clutch table. It should return a vector of 3, each with 3 elements
```{r}
Rawcombo<-function(Dataset){
  #read in the four pressure column situations
  BYUHold<-BYUHoldColumn(Dataset)[[1]]
  BYUBreak<-BYUBreakColumn(Dataset)[[1]]
  OppHold<-OppHoldColumn(Dataset)[[1]]
  OppBreak<-OppBreakColumn(Dataset)[[1]]
  
  #initialize and then fill in Rawcombocolumn
  Rawcombocolumn<-NULL

    Top<-BYUHold[1]+BYUBreak[1]
    Middle<-BYUHold[2]+BYUBreak[2]+OppHold[1]+OppBreak[1]
    Bottom<-BYUHold[3]+BYUBreak[3]+OppHold[2]+OppBreak[2]
  
  RawComboColumn<-c(Top,Middle,Bottom)
  
  NTop<-BYUHoldColumn(Dataset)[[2]][1]+BYUBreakColumn(Dataset)[[2]][1]
  NMiddle<-BYUHoldColumn(Dataset)[[2]][2] + BYUBreakColumn(Dataset)[[2]][2] + OppHoldColumn(Dataset)[[2]][1] + OppBreakColumn(Dataset)[[2]][1]
  NBottom<-BYUHoldColumn(Dataset)[[2]][3] + BYUBreakColumn(Dataset)[[2]][3] + OppHoldColumn(Dataset)[[2]][2] + OppBreakColumn(Dataset)[[2]][2]
  
  RawComboN<-c(NTop, NMiddle, NBottom)
  
  Ans<-list(RawComboColumn, RawComboN)
  
  return(Ans)
}
```

The Weighted combo function takes a Dataset and a weight vector of length 12 it can apply to each combination of OPP/BYU/Hold/Break being Clutch, Choke or neutral. It doesn't account for specific high-stress points, like a match points vs. a Hold point in the first set. 
```{r}
#It's jacked up. This needs some fixing with list being put into serving and play scores
wcombo<-function(Dataset,Weights=c(rep(1,times=12))){
  #read in the four pressure column situations
  BYUHold<-BYUHoldColumn(Dataset)[[1]]
  BYUBreak<-BYUBreakColumn(Dataset)[[1]]
  OppHold<-OppHoldColumn(Dataset)[[1]]
  OppBreak<-OppBreakColumn(Dataset)[[1]]
  
  #initialize and then fill in Rawcombocolumn
  WComboColumn<-NULL
  
    S<-Weights[1]*unlist(BYUHold[1])[1]+Weights[2]*unlist(BYUBreak[1])[1]
    P<-Weights[5]*unlist(BYUHold[1])[2]+Weights[6]*unlist(BYUBreak[1])[2]
    C<-Weights[9]*unlist(BYUHold[1])[3]+Weights[10]*unlist(BYUBreak[1])[3]
    Top<-c(S,P,C)
    
    S<-Weights[1]*unlist(BYUHold[2])[1]+Weights[2]*unlist(BYUBreak[2])[1]+Weights[3]*unlist(OppHold[1])[1]+Weights[4]*unlist(OppBreak[1])[1]
    P<-Weights[5]*unlist(BYUHold[2])[2]+Weights[6]*unlist(BYUBreak[2])[2]+Weights[7]*unlist(OppHold[1])[2]+Weights[8]*unlist(OppBreak[1])[2]
    C<-Weights[9]*unlist(BYUHold[2])[3]+Weights[10]*unlist(BYUBreak[2])[3]+Weights[11]*unlist(OppHold[1])[3]+Weights[12]*unlist(OppBreak[1])[3]
    Middle<-c(S,P,C)
    
    S<-Weights[1]*unlist(BYUHold[3])[1]+Weights[2]*unlist(BYUBreak[3])[1]+Weights[3]*unlist(OppHold[2])[1]+Weights[4]*unlist(OppBreak[2])[1]
    P<-Weights[5]*unlist(BYUHold[3])[2]+Weights[6]*unlist(BYUBreak[3])[2]+Weights[7]*unlist(OppHold[2])[2]+Weights[8]*unlist(OppBreak[2])[2]
    C<-Weights[9]*unlist(BYUHold[3])[3]+Weights[10]*unlist(BYUBreak[3])[3]+Weights[11]*unlist(OppHold[2])[3]+Weights[12]*unlist(OppBreak[2])[3]
    Bottom<-c(S,P,C)
  
  WComboColumn<-list(Top,Middle,Bottom)
  return(WComboColumn)
}
```


fullanalysismatrix calls all our previous functions and turns them into a matrix that looks like our table we have under Clutch analysis
```{r}
FullClutchMatrix<-function(Dataset){
  #Format the Matrix
  MATRIX<-matrix(data=0,nrow=3,ncol = 6)
  rownames(MATRIX)<-c("Clutch Serving Score","Clutch Playing Score", "Overall Clutch Score")
  colnames(MATRIX)<-c("Low Pressure","BYU Hold", "BYU Break", "Opp Hold", "Opp Break", "Combo")
  
  #Make the LP matrix and do the non-Clutch column
  LPDataset<-LPcolumn(Dataset)
  MATRIX[,1]<-round(LPDataset[[1]]/LPDataset[[2]], digits = 7)
  
  #Then the next 4 columns
  HPDataset<-HighPressure(Dataset)
  MATRIX[,2]<-round(BYUHoldColumn(HPDataset)[[1]]/BYUHoldColumn(HPDataset)[[2]], digits = 7)
  MATRIX[,3]<-round(BYUBreakColumn(HPDataset)[[1]]/BYUBreakColumn(HPDataset)[[2]], digits = 7)
  MATRIX[2:3,4]<-round(OppHoldColumn(HPDataset)[[1]]/OppHoldColumn(HPDataset)[[2]], digits = 7)
  MATRIX[2:3,5]<-round(OppBreakColumn(HPDataset)[[1]]/OppHoldColumn(HPDataset)[[2]], digits = 7)
  MATRIX[,6]<-round(Rawcombo(HPDataset)[[1]]/Rawcombo(HPDataset)[[2]], digits = 7)
  MATRIX[1,4:5]<-c(NA,NA)
  MATRIX<-as.data.frame.matrix(MATRIX)
  return(MATRIX)
}
```

FormatData: Does all the formating we need before throwing it in FullMatrix
```{r}
FormatData<-function(RawData,DataType="OldSQL"){
  if(DataType=="NewExcel"){
    JointData<-(cbind(RawData[,c(11,12,14:16,18:24,32)],rep(0,length=dim(RawData)[1])))
  }
  if(DataType=="OldSQL"){
    JointData<-(cbind(RawData[,c(12:13,15:17,19:25,33)],rep(0,length=dim(RawData)[1])))
  }
  colnames(JointData)<-c("PlayerSets","OppSets","PlayerGames","OppGames","Server", "PlayerPoints", "OppPoints", "ServeResult", "ServeLocation", "ReturnLocation", "Result", "PointWinner", "PointLength","SituationalWeight")
  JointData<-SetScoreCorrector(JointData)
  JointData<-as.tbl(JointData)
  JointData$SituationalWeight<-SituationalWeights(JointData)
  return(JointData)
}

```


Here we'll create the table after inputting just the RawData
```{r}
ClutchTableMaker<-function(RawData){
  FData<-FormatData(RawData)
  TabData<-FullClutchMatrix(FData)
  
  #Start the gt
  FinTable<-gt(TabData, rownames_to_stub = TRUE)
  
  #add the header, with names varying on whether on not there's multiple people in the table to make
  Names<-unique(RawData$PlayerID)
  
  #for
  
  if (length(Names)==1){
    FinTable <-
      tab_header(data = FinTable,
    title = "Clutch Scoring Table",
    subtitle = paste(Names, "data from", min(as.Date(RawData$Date,"%m/%d/%Y")), "to", max(as.Date(RawData$Date,"%m/%d/%Y"))))
  }
  
  #Assigning the values for our domains
  LP<-c(-.2,.2)
  BH<-c(-.5,1)
  BB<-c(-.64,1)
  OH<-c(-.5,.3)
  OB<-c(-.5,.3)
  C<-c(-1,1)

  #Coloring the columns in order, using the values we chose earlier for highs and lows
  FinTable<-data_color(FinTable,columns = "Low Pressure", colors = scales::col_numeric(palette = "RdYlGn", domain = LP))
  FinTable<-data_color(FinTable,columns = "BYU Hold", colors = scales::col_numeric(palette = "RdYlGn", domain = BH))
  FinTable<-data_color(FinTable,columns = "BYU Break", colors = scales::col_numeric(palette = "RdYlGn", domain = BB))
  FinTable<-data_color(FinTable,columns = "Opp Hold", colors = scales::col_numeric(palette = "RdYlGn", domain = OH))
  FinTable<-data_color(FinTable,columns = "Opp Break", colors = scales::col_numeric(palette = "RdYlGn", domain = OB))
  FinTable<-data_color(FinTable,columns = "Combo", colors = scales::col_numeric(palette = "RdYlGn", domain = C))  
      
  return(FinTable)
}
```



~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~WORKING EXAMPLES~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

~~~~~~~~~~~~~~~~~~~~Now's let's work with the Women's Data already collected~~~~~~~~~~~~~~~~~~~~~~
All the Women's Data Together runs, as well as individual players' data

```{r}
AllData<-rbind(read.csv("Women's Player Data Files/MJones18.csv"),
               read.csv("Women's Player Data Files/AAbramyan18.csv"),
               read.csv("Women's Player Data Files/KCusick18.csv"),
               read.csv("Women's Player Data Files/PMalykh18.csv"),
               read.csv("Women's Player Data Files/SSmith18.csv"),
               read.csv("Women's Player Data Files/HKaur18.csv"))


(AllTable<-ClutchTableMaker(AllData))
(MJones<-ClutchTableMaker(read.csv("Women's Player Data Files/MJones18.csv")))
(AAbramyan<-ClutchTableMaker(read.csv("Women's Player Data Files/AAbramyan18.csv")))
(KCusick<-ClutchTableMaker(read.csv("Women's Player Data Files/KCusick18.csv")))
(PMalykh<-ClutchTableMaker(read.csv("Women's Player Data Files/PMalykh18.csv")))
(SSmith<-ClutchTableMaker(read.csv("Women's Player Data Files/SSmith18.csv")))
(HKaur<-ClutchTableMaker(read.csv("Women's Player Data Files/HKaur18.csv")))
```
Playing with Bootstrapping
```{r}
BootStrapSim<-function(AllData, PlayerData, Reps){
  N<-dim(AllData)[1]
  n<-dim(PlayerData)[1]
  LPSV<-vector()
  LPPV<-vector()
  LPCV<-vector()
  BHSV<-vector()
  BHPV<-vector()
  BHCV<-vector()
  BBSV<-vector()
  BBPV<-vector()
  BBCV<-vector()
  OHSV<-vector()
  OHPV<-vector()
  OHCV<-vector()
  OBSV<-vector()
  OBPV<-vector()
  OBCV<-vector()
  CSV<-vector()
  CPV<-vector()
  CCV<-vector()

  for(i in 1:Reps){
    #Build randomized matrix
    RandyNum<-sample(1:N,n)
    Dataset<-AllData[RandyNum,]
    FDataset<-FormatData(Dataset)
    RandyResult<-FullClutchMatrix(FDataset)
    LPSV[i]<-RandyResult$`Low Pressure`[1]
    LPPV[i]<-RandyResult$`Low Pressure`[2]
    LPCV[i]<-RandyResult$`Low Pressure`[3]
    BHSV[i]<-RandyResult$`BYU Hold`[1]
    BHPV[i]<-RandyResult$`BYU Hold`[2]
    BHCV[i]<-RandyResult$`BYU Hold`[3]
    BBSV[i]<-RandyResult$`BYU Break`[1]
    BBPV[i]<-RandyResult$`BYU Break`[2]
    BBCV[i]<-RandyResult$`BYU Break`[3]
    OHSV[i]<-RandyResult$`Opp Hold`[1]
    OHPV[i]<-RandyResult$`Opp Hold`[2]
    OHCV[i]<-RandyResult$`Opp Hold`[3]
    OBSV[i]<-RandyResult$`Opp Break`[1]
    OBPV[i]<-RandyResult$`Opp Break`[2]
    OBCV[i]<-RandyResult$`Opp Break`[3]
    CSV[i]<-RandyResult$Combo[1]
    CPV[i]<-RandyResult$Combo[2]
    CCV[i]<-RandyResult$Combo[3]
  }
  
  PlayerMatrix<-FullClutchMatrix(FormatData(PlayerData))
    PLPSV<-PlayerMatrix$`Low Pressure`[1]
    PLPPV<-PlayerMatrix$`Low Pressure`[2]
    PLPCV<-PlayerMatrix$`Low Pressure`[3]
    PBHSV<-PlayerMatrix$`BYU Hold`[1]
    PBHPV<-PlayerMatrix$`BYU Hold`[2]
    PBHCV<-PlayerMatrix$`BYU Hold`[3]
    PBBSV<-PlayerMatrix$`BYU Break`[1]
    PBBPV<-PlayerMatrix$`BYU Break`[2]
    PBBCV<-PlayerMatrix$`BYU Break`[3]
    POHSV<-PlayerMatrix$`Opp Hold`[1]
    POHPV<-PlayerMatrix$`Opp Hold`[2]
    POHCV<-PlayerMatrix$`Opp Hold`[3]
    POBSV<-PlayerMatrix$`Opp Break`[1]
    POBPV<-PlayerMatrix$`Opp Break`[2]
    POBCV<-PlayerMatrix$`Opp Break`[3]
    PCSV<-PlayerMatrix$Combo[1]
    PCPV<-PlayerMatrix$Combo[2]
    PCCV<-PlayerMatrix$Combo[3]
  
  BootLPSV<-sum(LPSV<PLPSV)/Reps  
  BootLPPV<-sum(LPPV<PLPPV)/Reps 
  BootLPCV<-sum(LPCV<PLPCV)/Reps 
  BootBHSV<-sum(BHSV<PBHSV)/Reps 
  BootBHPV<-sum(BHPV<PBHPV)/Reps 
  BootBHCV<-sum(BHCV<PBHCV)/Reps 
  BootBBSV<-sum(BBSV<PBBSV)/Reps   
  BootBBPV<-sum(BBPV<PBBPV)/Reps 
  BootBBCV<-sum(BBCV<PBBCV)/Reps 
  BootOHSV<-sum(OHSV<POHSV)/Reps   
  BootOHPV<-sum(OHPV<POHPV)/Reps 
  BootOHCV<-sum(OHCV<POHCV)/Reps 
  BootOBSV<-sum(OBSV<POBSV)/Reps   
  BootOBPV<-sum(OBPV<POBPV)/Reps 
  BootOBCV<-sum(OBCV<POBCV)/Reps 
  BootCSV<-sum(CSV<PCSV)/Reps   
  BootCPV<-sum(CPV<PCPV)/Reps 
  BootCCV<-sum(CCV<PCCV)/Reps 
  
  BootMatrix<-cbind(as.numeric(c(BootLPSV, BootLPPV, BootLPCV)),
                    as.numeric(c(BootBHSV, BootBHPV, BootBHCV)),
                    as.numeric(c(BootBBSV, BootBBPV, BootBBCV)),
                    as.numeric(c("NA", BootOHPV, BootOHCV)),
                    as.numeric(c("NA", BootOBPV, BootOBCV)),
                    as.numeric(c(BootCSV, BootCPV, BootCCV)))
  colnames(BootMatrix)<-c("Low Pressure","BYU Hold","BYU Break","Opp Hold","Opp Break","Combo")
  rownames(BootMatrix)<-c("Clutch Serving Score", "Clutch Playing Score", "Combined Clutch Score")
  

  #Start the gt
  BootGT<-gt(as.data.frame( BootMatrix), rownames_to_stub = TRUE)
  
  #add the header, with names varying on whether on not there's multiple people in the table to make
  Names<-unique(PlayerData$PlayerID)
  
  #for
  
  if (length(Names)==1){
    BootGT <-
      tab_header(data = BootGT,
    title = "Clutch Scoring Table",
    subtitle = paste(Names, "data from", min(as.Date(PlayerData$Date,"%m/%d/%Y")), "to", max(as.Date(PlayerData$Date,"%m/%d/%Y"))))
  }
  
  #Assigning the values for our domains
  BaseCol<-c(0,1)

  #Coloring the columns in order, using the values we chose earlier for highs and lows
  (BootGT<-data_color(BootGT,columns = c("Combo", "Low Pressure", "BYU Hold", "BYU Break", "Opp Hold", "Opp Break"), colors = scales::col_numeric(palette = "RdYlGn", domain = BaseCol))) 
  
  return(BootGT)
  }
```

```{r}
HK18<-BootStrapSim(AllData,read.csv("Women's Player Data Files/HKaur18.csv"),100)
SS18<-BootStrapSim(AllData,read.csv("Women's Player Data Files/SSmith18.csv"),100)
AA18<-BootStrapSim(AllData,read.csv("Women's Player Data Files/AAbramyan18.csv"),100)
PM18<-BootStrapSim(AllData,read.csv("Women's Player Data Files/PMalykh18.csv"),100)
KC18<-BootStrapSim(AllData,read.csv("Women's Player Data Files/KCusick18.csv"),100)

HK18
```



RUNNING TO DO LIST:
- DO THE BOOTSTRAPPING TO EVALUATE EACH PLAYER'S PERFORMANCE
    - Why are the opp columns returning 0.00 everytime? 
- FIX MINOR COLORATION ISSUES
    - GT needs to be coloring specific cells, not the columns. We also need to assume all the data is normally distributed, which isn't necessarily true. 