---
title: "Serving Analyses"
author: "Othon Hamill"
date: "October 24, 2018"
output: word_document
---

Serves.rmd outputs the serves table we'll use in our presentation. There'a a long-long-long list of functions but the last chunk uses them all to output our table. 

################################TO-DO LIST##############################################
Probably want to build something that throws out incomplete data, or we can clean and check data before each calculation
We need a way to cut the end off of the excel data files we get from the matches. We could do it manually each time, or write a function to lop the end off of it each time. 

For the formatting of the tables:
  Look into formatable and xtable, Othon has the links sent to him from Prof. Blair, 
  Look more into having our rfile write directly into an excel document that could send data to be made into a excel table. That way we remain in excel for our output that we send to the tennis team. 

```{r}
#call our necessary libraries
library(alr3)
library(MASS)
library(dplyr)
```

###################  And the Functions begin  #############################

Set Score Corrector, for those situations where the set score doesn't get set back to 0-0 after a set is won
```{r}
SetScoreCorrector<-function(Data){
  N<-dim(Data)[1]
  Errors<-rep(0,times=N)
  
  #Here's our work for a win on the players side not being counted correctly
    for (i in 1:N){
        Errors[i]<- (Data$PlayerGames[i] >= 6 & Data$OppGames[i] < 5)
    }
  
    #here we correct the game/set scores. We make the assumption our Data has the sets correct
    Data$PlayerGames<-Data$PlayerGames-Errors*(6)
  
    return(Data)
}
```


Just BYU Serving
```{r}
PServingOnly<-function(RawData){
  Joint<-filter(RawData,RawData$Server=="P")
}
```

Deuce and Ad Creator
```{r}
DeuceAdCreator<-function(Joint, AdScoring = FALSE){
  #just Deuce points
  
if(AdScoring == T){
  Deuce<-rbind(Joint[(Joint$PlayerPoints+Joint$OppPoints %% 2) == 0,])
  Ad<-rbind(Joint[(Joint$PlayerPoints+Joint$OppPoints %% 2) == 1,])
}
  
else{
  Deuce<-rbind(
    Joint[Joint$PlayerPoints+Joint$OppPoints == 0,],
    Joint[Joint$PlayerPoints+Joint$OppPoints == 2,],
    Joint[Joint$PlayerPoints+Joint$OppPoints == 4,])

#just Ad points
  Ad<-rbind(
    Joint[Joint$PlayerPoints+Joint$OppPoints == 1,],
    Joint[Joint$PlayerPoints+Joint$OppPoints == 3,],
    Joint[Joint$PlayerPoints+Joint$OppPoints == 5,])
}
  
DAJlist<-list(Deuce,Ad,Joint)
return(DAJlist)
}
```


Court Distribution Calculator Function that creates the First row of the table
```{r}
CourtDistFunc<-function(Deuce,Ad,Joint)
{
  NDFDeuce<-sum(Deuce$ServeResult=="D")
  NDeuce<-dim(Deuce)[1]-NDFDeuce
  DW<-sum(Deuce$ServeLocation=="W")/NDeuce
  DB<-sum(Deuce$ServeLocation=="B")/NDeuce
  DL<-(sum(Deuce$ServeLocation%in%c("L","C","T")))/NDeuce
  
  NDFAd<-sum(Ad$ServeResult=="D")
  NAd<-dim(Ad)[1]-NDFAd
  AW<-sum(Ad$ServeLocation=="W")/NAd
  AB<-sum(Ad$ServeLocation=="B")/NAd
  AL<-(sum(Ad$ServeLocation%in%c("L","C","T")))/NAd
  
  NDFJoint<-sum(Joint$ServeResult=="D")
  NJoint<-dim(Joint)[1]-NDFJoint
  JW<-sum(Joint$ServeLocation=="W")/NJoint
  JB<-sum(Joint$ServeLocation=="B")/NJoint
  JL<-(sum(Joint$ServeLocation%in%c("L","C","T")))/NJoint
  
  
  CourtDistlist<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(CourtDistlist)
}
```

AcePercFunc gives us the percentages of shots to a given area that result in aces
```{r}
AcePercFunc<-function(Deuce,Ad,Joint)
{
    
  AJoint<-filter(Joint,Joint$ServeLocation%in%c("W", "B", "C", "L", "T"))
  NJoint<-dim(AJoint)[1]
  
  ADeuce<-filter(Deuce,Deuce$ServeLocation%in%c("W", "B", "C", "L", "T"))
  AAd<-filter(Ad,Ad$ServeLocation%in%c("W", "B", "C", "L", "T"))
  if(NJoint==0){
    DW<-DB<-DL<-AW<-AB<-AL<-JW<-JB<-JL<-0
  }
  else{
    DW<-sum(ADeuce$ServeLocation=="W")/NJoint
    DB<-sum(ADeuce$ServeLocation=="B")/NJoint
    DL<-sum(ADeuce$ServeLocation%in%c("L","C","T"))/NJoint
    AB<-sum(AAd$ServeLocation=="B")/NJoint
    AL<-sum(AAd$ServeLocation%in%c("L","C","T"))/NJoint
    AW<-sum(AAd$ServeLocation=="W")/NJoint
    JW<-sum(AJoint$ServeLocation=="W")/NJoint
    JB<-sum(AJoint$ServeLocation=="B")/NJoint
    JL<-sum(AJoint$ServeLocation%in%c("L","C","T"))/NJoint
  }

  AcePercList<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(AcePercList)
}
```


Ace Distribution Function
There's still an issue about how we select DW, DB and DL as 0. We need to make those 0 whenever Njoint euqals zero, otherwise we'll get an divide by zero error in that case. 
```{r}
AceDistFunc<-function(Deuce,Ad,Joint)
{
  AJoint<-filter(Joint,Joint$Result=="A" & Joint$ServeLocation%in%c("W", "B", "C", "L", "T"))
  NJoint<-dim(AJoint)[1]
  
  ADeuce<-filter(Deuce,Deuce$Result=="A")
  NDeuce<-dim(ADeuce)[1]
  if(NDeuce==0){
    DW<-DB<-DL<-0
  }
  else{
    DW<-sum(ADeuce$ServeLocation=="W")/NJoint
    DB<-sum(ADeuce$ServeLocation=="B")/NJoint
    DL<-sum(ADeuce$ServeLocation%in%c("L","C","T"))/NJoint
  }
 
  
  AAd<-filter(Ad,Ad$Result=="A")
  NAd<-dim(AAd)[1]
  if(NAd==0){
    AW<-AB<-AL<-0
  }
  else{
    AW<-sum(AAd$ServeLocation=="W")/NJoint
    AB<-sum(AAd$ServeLocation=="B")/NJoint
    AL<-sum(AAd$ServeLocation%in%c("L","C","T"))/NJoint
  }
  

  if(NJoint==0){
    JW<-JB<-JL<-0
  }
  else{
    JW<-sum(AJoint$ServeLocation=="W")/NJoint
    JB<-sum(AJoint$ServeLocation=="B")/NJoint
    JL<-sum(AJoint$ServeLocation%in%c("L","C","T"))/NJoint
  }
  
  
  AceProbList<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(AceProbList)
}
```


Short Game Win Percentage Calculator
```{r}
ShortGameWinPerc<-function(Deuce,Ad,Joint)
{
  
  SDeuce<-filter(Deuce,Deuce$PointLength=="S")
  SWinDeuce<-filter(SDeuce,SDeuce$PointWinner=="P")
  SWinDeuce<-as.tbl(SWinDeuce)
  DW<-sum(SWinDeuce$ServeLocation=="W")/sum(SDeuce$ServeLocation=="W")
  DB<-sum(SWinDeuce$ServeLocation=="B")/sum(SDeuce$ServeLocation=="B")
  DL<-sum(SWinDeuce$ServeLocation%in%c("L","C","T"))/sum(SDeuce$ServeLocation%in%c("L","C","T"))
  
  SAd<-filter(Ad,Ad$PointLength=="S")
  SWinAd<-filter(SAd,SAd$PointWinner=="P")
  SWinAd<-as.tbl(SWinAd)
  AW<-sum(SWinAd$ServeLocation=="W")/sum(SAd$ServeLocation=="W")
  AB<-sum(SWinAd$ServeLocation=="B")/sum(SAd$ServeLocation=="B")
  AL<-sum(SWinAd$ServeLocation%in%c("L","C","T"))/sum(SAd$ServeLocation%in%c("L","C","T"))
  
  SJoint<-filter(Joint,Joint$PointLength=="S")
  swiNJoint<-filter(SJoint,SJoint$PointWinner=="P")
  swiNJoint<-as.tbl(swiNJoint)
  JW<-sum(swiNJoint$ServeLocation=="W")/sum(SJoint$ServeLocation=="W")
  JB<-sum(swiNJoint$ServeLocation=="B")/sum(SJoint$ServeLocation=="B")
  JL<-sum(swiNJoint$ServeLocation%in%c("L","C","T"))/sum(SJoint$ServeLocation%in%c("L","C","T"))
  
  
  ShortGameWinPerclist<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(ShortGameWinPerclist)
}
```

First Serve Placement Calculator
```{r}
FirstCourtDist<-function(Deuce,Ad,Joint)
{
  FDeuce<-filter(Deuce,Deuce$ServeResult=="F")
  NFDeuce<-dim(FDeuce)[1]
  DW<-sum(FDeuce$ServeLocation=="W")/NFDeuce
  DB<-sum(FDeuce$ServeLocation=="B")/NFDeuce
  DL<-(sum(FDeuce$ServeLocation%in%c("L","C","T")))/NFDeuce
  
  FAd<-filter(Ad,Ad$ServeResult=="F")
  NFAd<-dim(FAd)[1]
  AW<-sum(FAd$ServeLocation=="W")/NFAd
  AB<-sum(FAd$ServeLocation=="B")/NFAd
  AL<-(sum(FAd$ServeLocation%in%c("L","C","T")))/NFAd
  
  FJoint<-filter(Joint,Joint$ServeResult=="F")
  NFJoint<-dim(FJoint)[1]
  JW<-sum(FJoint$ServeLocation=="W")/NFJoint
  JB<-sum(FJoint$ServeLocation=="B")/NFJoint
  JL<-(sum(FJoint$ServeLocation%in%c("L","C","T")))/NFJoint
  
  
  FirstCourtDistlist<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(FirstCourtDistlist)
}
```

Second Serve Placement Calculator
```{r}
SecondCourtDist<-function(Deuce,Ad,Joint)
{
  SDeuce<-filter(Deuce,Deuce$ServeResult=="S")
  NSDeuce<-dim(SDeuce)[1]
  DW<-sum(SDeuce$ServeLocation=="W")/NSDeuce
  DB<-sum(SDeuce$ServeLocation=="B")/NSDeuce
  DL<-(sum(SDeuce$ServeLocation%in%c("L","C","T")))/NSDeuce
  
  SAd<-filter(Ad,Ad$ServeResult=="S")
  NSAd<-dim(SAd)[1]
  AW<-sum(SAd$ServeLocation=="W")/NSAd
  AB<-sum(SAd$ServeLocation=="B")/NSAd
  AL<-(sum(SAd$ServeLocation%in%c("L","C","T")))/NSAd
  
  SJoint<-filter(Joint,Joint$ServeResult=="S")
  NSJoint<-dim(SJoint)[1]
  JW<-sum(SJoint$ServeLocation=="W")/NSJoint
  JB<-sum(SJoint$ServeLocation=="B")/NSJoint
  JL<-(sum(SJoint$ServeLocation%in%c("L","C","T")))/NSJoint
  
  
  SecondCourtDistlist<-c(DW,DB,DL,AL,AB,AW,JL,JB,JW)
  return(SecondCourtDistlist)
}
```

Under Pressure Calculator. Doesnt work if there's dividing by 0 issues. NPDeuce is usually the culprit.
Here's the defending side of the problem. Notice we include deuce as being a defending situation. BYU would "defend" their serve, not attack it. You'd attack a break point. 
```{r}
DefPressureDistribution<-function(Deuce, Ad, Joint,FSWeights=c(1,1)){
  PDeuce<-filter(Deuce,Deuce$ServeResult%in%c("F", "S") &
                        Deuce$PlayerPoints==1 & Deuce$OppPoints==3)
  NPDeuce<-sum(PDeuce$ServeResult=="F")*FSWeights[1]+sum(PDeuce$ServeResult=="S")*FSWeights[2]
  DW<-(sum(PDeuce$ServeLocation=="W" & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation=="W" & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  DB<-(sum(PDeuce$ServeLocation=="B" & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation=="B" & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  DL<-(sum(PDeuce$ServeLocation%in%c("L","C","T") & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation%in%c("L","C","T") & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  
  PAd<-filter(Ad,Ad$ServeResult%in%c("F", "S") & (
                        Ad$PlayerPoints==2 & Ad$OppPoints==3 |
                        Ad$PlayerPoints==0 & Ad$OppPoints==3))
  NPAd<-sum(PAd$ServeResult=="F")*FSWeights[1]+sum(PAd$ServeResult=="S")*FSWeights[2]
  AW<-(sum(PAd$ServeLocation=="W" & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation=="W" & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  AB<-(sum(PAd$ServeLocation=="B" & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation=="B" & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  AL<-(sum(PAd$ServeLocation%in%c("L","C","T") & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation%in%c("L","C","T") & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  
  PJoint<-filter(Joint,Joint$ServeResult%in%c("F", "S") & (
                        Joint$PlayerPoints==3 & Joint$OppPoints==3 |
                        Joint$PlayerPoints==2 & Joint$OppPoints==3 |
                        Joint$PlayerPoints==1 & Joint$OppPoints==3 |
                        Joint$PlayerPoints==0 & Joint$OppPoints==3))
  NPJoint<-sum(PJoint$ServeResult=="F")*FSWeights[1]+sum(PJoint$ServeResult=="S")*FSWeights[2]
  JW<-(sum(PJoint$ServeLocation=="W" & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation=="W" & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  JB<-(sum(PJoint$ServeLocation=="B" & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation=="B" & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  JL<-(sum(PJoint$ServeLocation%in%c("L","C","T") & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation%in%c("L","C","T") & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  
  
  DefPressureDistlist<-c(DW, DB, DL, AL, AB, AW, JL, JB, JW)
  return(DefPressureDistlist)
}
```
Here's the attacking side of that problem
```{r}
AtkPressureDistribution<-function(Deuce, Ad, Joint,FSWeights=c(1,1)){
  PDeuce<-filter(Deuce,Deuce$ServeResult%in%c("F", "S") &
                        Deuce$PlayerPoints==3 & Deuce$OppPoints==1)
  NPDeuce<-sum(PDeuce$ServeResult=="F")*FSWeights[1]+sum(PDeuce$ServeResult=="S")*FSWeights[2]
  DW<-(sum(PDeuce$ServeLocation=="W" & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation=="W" & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  DB<-(sum(PDeuce$ServeLocation=="B" & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation=="B" & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  DL<-(sum(PDeuce$ServeLocation%in%c("L","C","T") & PDeuce$ServeResult=="F") * FSWeights[1] +               sum(PDeuce$ServeLocation%in%c("L","C","T") & PDeuce$ServeResult=="S") * FSWeights[2]) /NPDeuce
  PAd<-filter(Ad,Ad$ServeResult%in%c("F", "S") & (
                        Ad$PlayerPoints==3 & Ad$OppPoints==2 |
                        Ad$PlayerPoints==3 & Ad$OppPoints==0))
  NPAd<-sum(PAd$ServeResult=="F")*FSWeights[1]+sum(PAd$ServeResult=="S")*FSWeights[2]
  AW<-(sum(PAd$ServeLocation=="W" & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation=="W" & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  AB<-(sum(PAd$ServeLocation=="B" & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation=="B" & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  AL<-(sum(PAd$ServeLocation%in%c("L","C","T") & PAd$ServeResult=="F") * FSWeights[1] +               sum(PAd$ServeLocation%in%c("L","C","T") & PAd$ServeResult=="S") * FSWeights[2]) /NPAd
  
  PJoint<-filter(Joint,Joint$ServeResult%in%c("F", "S") & (
                        Joint$PlayerPoints==3 & Joint$OppPoints==2 |
                        Joint$PlayerPoints==3 & Joint$OppPoints==1 |
                        Joint$PlayerPoints==3 & Joint$OppPoints==0))
  NPJoint<-sum(PJoint$ServeResult=="F")*FSWeights[1]+sum(PJoint$ServeResult=="S")*FSWeights[2]
  JW<-(sum(PJoint$ServeLocation=="W" & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation=="W" & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  JB<-(sum(PJoint$ServeLocation=="B" & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation=="B" & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  JL<-(sum(PJoint$ServeLocation%in%c("L","C","T") & PJoint$ServeResult=="F") * FSWeights[1] +               sum(PJoint$ServeLocation%in%c("L","C","T") & PJoint$ServeResult=="S") * FSWeights[2]) /NPJoint
  
  
  AtkPressureDistlist<-c(DW, DB, DL, AL, AB, AW, JL, JB, JW)
  return(AtkPressureDistlist)
}
```

Double Fault Percentage Calculator
```{r}
DFPerc<-function(Deuce,Ad,Joint)
{
  NDFDeuce<-sum(Deuce$ServeResult=="D")
  NDeuce<-dim(Deuce)[1]
  DFD<-NDFDeuce/NDeuce
  
  NDFAd<-sum(Ad$ServeResult=="D")
  NAd<-dim(Ad)[1]
  DFA<-NDFAd/NAd
  
  NDFJoint<-sum(Joint$ServeResult=="D")
  NJoint<-dim(Joint)[1]
  DFJ<-NDFJoint/NJoint
  
  
  DFList<-c(rep(DFD,times=3),rep(DFA,times=3),rep(DFJ,times=3))
  return(DFList)
}
```

Situational Weights Adds an Additional column which gives a weight score for each point
40-00 gets a .3 multiplier, 40-15 a .7, 40-30 a 1.0, Deuce a 2x
4-4 and 5-5 get a x1.5 multiplier
Set Points get x2
Second Set Match Points get a x3 Multiplier
Third Set Match Points get a x3 Multiplier

5-4, 4-5, 6-5 and 5-6 gets a +1


```{r}
SituationalWeights<-function(Data){
  N<-dim(Data)[1]
  Multiplier<-rep(0,times=N)
  
  #Game Points by score weight
  for (i in 1:N){
    if(Data$PlayerPoints[i] == 0 & Data$OppPoints[i] == 3){Multiplier[i]<-.3}
    if(Data$OppPoints[i] == 0 & Data$PlayerPoints[i] == 3){Multiplier[i]<-.3}
    if(Data$PlayerPoints[i] == 1 & Data$OppPoints[i] == 3){Multiplier[i]<-.7}
    if(Data$OppPoints[i] == 1 & Data$PlayerPoints[i] == 3){Multiplier[i]<-.7}
    if(Data$PlayerPoints[i] == 2 & Data$OppPoints[i] == 3){Multiplier[i]<-1}
    if(Data$OppPoints[i] == 2 & Data$PlayerPoints[i] == 3){Multiplier[i]<-1}
    if(Data$PlayerPoints[i] == 3 & Data$OppPoints[i] == 3){Multiplier[i]<-2}
  }
  
  #Game points under duress at 4-4 or 5-5 set score. High Pressure alreAdy keeps only game points
  for (i in 1:N){
    if(Data$PlayerGames[i] == 4 & Data$OppGames[i] == 4){Multiplier[i]<-Multiplier[i]*1.5}
    if(Data$OppGames[i] == 5 & Data$PlayerGames[i] == 5){Multiplier[i]<-Multiplier[i]*1.5}
  }

  #Set Points, 1st set about to be won by either or Second about to be won by the loser of the First set
  for (i in 1:N){
    #opp about to win the set
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0)) & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2}
    #player about to win the set
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*2+1}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*2}
    if(((Data$PlayerSets[i] == 0 & Data$OppSets[i] == 0) | (Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1)) & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*2}
  }
  
  #Match Points in the Second set
  for(i in 1:N){
    #player about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 0 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*3}
    #opponent about to win
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3+1}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
    if(Data$PlayerSets[i] == 0 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*3}
  }
  
  #Match Points in the Third set
  for(i in 1:N){
    #player about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 6 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 4) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 3) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 2) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 1) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 0) {Multiplier[i]<-Multiplier[i]*5}
    #opponent about to win
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 5 & Data$OppGames[i] == 6) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 4 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5+1}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 3 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 2 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 1 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
    if(Data$PlayerSets[i] == 1 & Data$OppSets[i] == 1 & Data$PlayerGames[i] == 0 & Data$OppGames[i] == 5) {Multiplier[i]<-Multiplier[i]*5}
  }
  
  return(Multiplier)
}

```

Serving Scoring Function
```{r}
ServingSore<-function(DataSet, W=c(1,-1,0)){
  Clutch<-rbind(filter(DataSet,DataSet$PointWinner=="P" & DataSet$PointLength=="S" & DataSet$Result %in% c("W","F") & DataSet$Server=="P"), filter(DataSet, DataSet$Result=="A" & DataSet$Server=="P"))
  Choke<-rbind(filter(DataSet,DataSet$PointWinner=="O" & DataSet$PointLength=="S" & DataSet$Result %in% c("W","F") & DataSet$Server=="P"), filter(DataSet, DataSet$Result=="D" & DataSet$Server=="P"))
  Null<-rbind(filter(DataSet, DataSet$ServeResult %in% c("F","S") & DataSet$PointLength %in% c("M","L") & DataSet$Server=="P"))
  #we Add an if here to catch when we run the LPcolum through Serving, sicne the situational weights of low pressure situations are 0. Here, if we find all the values are 0 we just use the dimensions in the calculation
  if(sum(Clutch$SituationalWeight)+sum(Choke$SituationalWeight)+sum(Null$SituationalWeight) == 0){
    Score<-dim(Clutch)[1]*W[1]+dim(Choke)[1]*W[2]+dim(Null)[1]*W[3]
  }
  else{
    Score<-c(sum(Clutch$SituationalWeight)*W[1]+sum(Choke$SituationalWeight)*W[2]+sum(Null$SituationalWeight)*W[3])
  }
  
  return(Score)
}
```

Serving Score Applied to W/B/L D/A/J
```{r}
AppliedScoring<-function(Deuce, Ad, Joint, W=c(1,-1,0) ){
  DW<-ServingSore(filter(Deuce, Deuce$ServeLocation=="W"))
  DB<-ServingSore(filter(Deuce, Deuce$ServeLocation=="B"))
  DL<-ServingSore(filter(Deuce, Deuce$ServeLocation=="L"))
  AW<-ServingSore(filter(Ad, Ad$ServeLocation=="W"))
  AB<-ServingSore(filter(Ad, Ad$ServeLocation=="B"))
  AL<-ServingSore(filter(Ad, Ad$ServeLocation%in%c("L","C","T")))
  JW<-ServingSore(filter(Joint, Joint$ServeLocation=="W"))
  JB<-ServingSore(filter(Joint, Joint$ServeLocation=="B"))
  JL<-ServingSore(filter(Joint, Joint$ServeLocation%in%c("L","C","T")))
  AppliedScores<-c(DW, DB, DL, AL, AB, AW, JL, JB, JW)
  return(AppliedScores)
}
```

FormatData: Does all the formating we need before throwing it in FullServeMatrix
NewExcel doesn't sort by Player ID
OldSQL includes player ID but doesn't sort by it, sino just puts it all together and leaves a new variable called PlayerID
```{r}
FormatData<-function(RawData,DataType="OldSQL"){
  if(DataType=="NewExcel"){
    JointData<-(cbind(RawData[,c(11,12,14:16,18:24,32)],rep(0,length=dim(RawData)[1])))
  }
  if(DataType=="OldSQL"){
    JointData<-(cbind(RawData[,c(12:13,15:17,19:25,33)],rep(0,length=dim(RawData)[1])))
  }
  colnames(JointData)<-c("PlayerSets","OppSets","PlayerGames","OppGames","Server", "PlayerPoints", "OppPoints", "ServeResult", "ServeLocation", "ReturnLocation", "Result", "PointWinner", "PointLength","SituationalWeight")
  JointData<-SetScoreCorrector(JointData)
  JointData<-as.tbl(JointData)
  JointData$SituationalWeight<-SituationalWeights(JointData)
  return(JointData)
}
```

Prepare the full matrix before we throw it into a table
NOTE: This doesn't run with player ID included
```{r}
FullServeMatrix<-function(DataSet,DataType="OldSQL"){
  #Format the Matrix
  MATRIX<-matrix(data=0,nrow=10,ncol = 9)
  rownames(MATRIX)<-c("Distribution", "First Serve Distribution", "Second Serve Distribution", "Double Fault %", "Def Pressure %", "Atk Pressure %", "Ace Distribution", "Ace Probability", "Short Game Win %", "Weighted Clutch Serving Score")

  ServingData<-PServingOnly(DataSet)
  colnames(ServingData)<-c("PlayerSets","OppSets","PlayerGames","OppGames","Server", "PlayerPoints", "OppPoints", "ServeResult", "ServeLocation", "ReturnLocation", "Result", "PointWinner", "PointLength")
    
  ServingData<-cbind(ServingData,SituationalWeights(ServingData))
  colnames(ServingData)<-c("PlayerSets","OppSets","PlayerGames","OppGames","Server", "PlayerPoints", "OppPoints", "ServeResult", "ServeLocation", "ReturnLocation", "Result", "PointWinner", "PointLength", "SituationalWeights")
  DAJ<-DeuceAdCreator(ServingData)
    Deuce<-as.data.frame(DAJ[1])
    Ad<-as.data.frame(DAJ[2])
    Joint<-as.data.frame(DAJ[3])
    
  MATRIX[1,]<-CourtDistFunc(Deuce,Ad,Joint)
  MATRIX[2,]<-FirstCourtDist(Deuce,Ad,Joint)
  MATRIX[3,]<-SecondCourtDist(Deuce,Ad,Joint)
  MATRIX[4,]<-DFPerc(Deuce,Ad,Joint)
  MATRIX[5,]<-DefPressureDistribution(Deuce,Ad,Joint)
  MATRIX[6,]<-AtkPressureDistribution(Deuce,Ad,Joint)
  MATRIX[7,]<-AceDistFunc(Deuce,Ad,Joint)
  MATRIX[8,]<-AcePercFunc(Deuce,Ad,Joint)
  MATRIX[9,]<-ShortGameWinPerc(Deuce,Ad,Joint)
  MATRIX[10,]<-AppliedScoring(Deuce,Ad,Joint)
  
  colnames(MATRIX)<-c("DWide", "DBody", "DT", "AT", "ABody", "AWide", "CT", "CBody", "CWide")
  
  return(MATRIX)
}
```

```{r}
ServeTableMaker<-function(RawData){
  FData<-FormatData(RawData)
  TabData<-FullServeMatrix(FData)
  
  #Start the gt
  FinTable<-gt(TabData, rownames_to_stub = TRUE)
  
  #add the header, with names varying on whether on not there's multiple people in the table to make
  Names<-unique(RawData$PlayerID)
  
  if (length(Names)==1){
    FinTable <-
      tab_header(data = FinTable,
    title = "Serving Table",
    subtitle = paste(Names, "data from", min(as.Date(RawData$Date)), "to", max(as.Date(RawData$Date))))
  }
  else{
    FinTable<-tab_header(data = FinTable, title = "Mass Serving Table")
  }

  Even<-c(0,30)

  #Coloring the columns in order, using the values we chose earlier for highs and lows
  
    #Assigning the values for our domains
  ZeroToOne<-c(0,1)

  #Coloring the columns in order, using the values we chose earlier for highs and lows
  #FinTable<-data_color(FinTable,columns = "DWide", colors = scales::col_numeric(palette = "RdYlGn", domain = ZeroToOne))
      
  return(FinTable)
}
```

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Here's our workspace after all the Functions~~~~~~~~~~~~~~~~~~~~~~~~

```{r}
AllData<-rbind(read.csv("Women's Player Data Files/MJones.csv"),
               read.csv("Women's Player Data Files/AAbramyan.csv"),
               read.csv("Women's Player Data Files/KCusick.csv"),
               read.csv("Women's Player Data Files/PMalykh.csv"),
               read.csv("Women's Player Data Files/SSmith.csv"))



ServeTableMaker(AllData)
```

RUNNING TO DO LIST:
- Resolve the coloring issues
- Bootstrap replacement values from out total sets. 




